manuscript - APP

### 2018-07-02 R/manuscript_app.Rmd
finish code polishing

---
title: "manuscript - JEP:HPP"
author: "Filip Dechterenko"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

@@

```{r load libraries}
here::set_here("../data")

@@

@@

```{r load data - exp 1a}
df_exp1a <- readRDS(here::here("..","data","exp1a","responses","responses_150330.rds")) %>% 
  filter(block != 0) %>% 
  filter(restk != "64") %>% # originally, we colledcted three levels of variaiblity, but the condition with kappa=64 showed similar results as kappa = 16
  as_data_frame() %>% 
  mutate(restk2 = recode(restk, `4` = "Brownian-like", `16` = "Ballistic-like"))

participants_exp1a <- read.csv(here::here("..","data","exp1a","participants_150526.csv"))

@@

```{r}
df_exp1a %>% 
  group_by(restk) %>% 
  summarize(accuracy_mean = mean(accuracy, na.rm = T)) %>% 
  knitr::kable(digits = 2)

@@

```{r Figure 1}
traj_k64 <- read.table("../data/exp1/trajectories/T001_64_rest4.csv") %>% select(x = V1,y = V2) %>% as_data_frame()
p1 <- traj_k64 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15) +
  ggtitle("Ballistic-like")

traj_k4 <- read.table("../data/exp1/trajectories/T001_4_rest4.csv") %>% select(x = V3,y = V4) %>% as_data_frame()
p2 <- traj_k4 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15)+
  ggtitle("Brownian-like")
gridExtra::grid.arrange(p1,p2, ncol = 2)
ggsave("Figure1_ballistic.png", p1, width = 6, height = 6)
ggsave("Figure1_brownian.png", p2, width = 6, height = 6)
ggsave("Figure1_ballistic.eps", p1, width = 6, height = 6)
ggsave("Figure1_brownian.eps", p2, width = 6, height = 6)
```

@@

plot_fig2 <- function(restk_var, ggtit) {
  df_exp1a %>%
  filter(restk == restk_var) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,8,16,32,64,128),labels = c("1","8","16","32","64","128"), trans = "log2") + 
  geom_vline(xintercept = restk_var, linetype = 2) +
  ggtitle(ggtit)
}

@@

ggsave("plots/Figure2_brownian.png", p1, width = 6, height = 6)
ggsave("plots/Figure2_ballistic.png", p2, width = 6, height = 6)
ggsave("plots/Figure2_brownian.eps", p1, width = 6, height = 6)
ggsave("plots/Figure2_ballistic.eps", p2, width = 6, height = 6)
```

```{r fitting weibull}

@@

```{r}
df_exp1 %>% 
  filter(restk2 == "Brownian-like") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

df_exp1 %>% 
  filter(restk2 == "Ballistic-like") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()
```

@@

```{r}
df_exp1a %>% 
  group_by(type, restk,subject) %>% 
  summarize(accuracy = mean(accuracy)) %>% 
  group_by(restk, type) %>% 
  filter(accuracy < 1) %>% 
  do(t.test(.$accuracy, mu = .125) %>% 
       broom::tidy()) %>% 
  mutate(p.value = round(p.value, 3)) %>% 
  knitr::kable()
```

## Difference between symmetrical cases
```{r}
df_exp1a %>% 
  filter((restk == 4 & type == 16) |(restk == 16 & type == 4)) %>% 
  ez::ezANOVA(
        dv = accuracy,
        wid = subject,
        within = restk, 
        detailed = T) %>% 
  apa::anova_apa()

@@

```{r load data - experiment 1b}
load(here::here("..","data","exp1b","responses","responses_150622.RData"))
df_exp1b <- filter(df, block != 0)

participants_exp2 <- read.csv(here::here("..","data","exp1b","participants_150526.csv"), fileEncoding = "UTF8")

@@

## Participant info
```{r}
table(participants_exp2$gender)
c(mean(participants_exp2$age), sd(participants_exp2$age)) %>% round(2)
```

@@

```{r plots experiment 2}
plot_fig3 <- function(restk_var, show_legend = F) {

  p <- df2_exp1b %>%
  filter(restk == restk_var) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous(expression("Variable"~kappa~" (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
  scale_linetype_manual(values = c(2,1)) +
  geom_vline(xintercept = restk_var, linetype = 2) +
  ggtitle(bquote("Fixed "~kappa~"= "~.(restk_var)))

  if (show_legend) {
    p 
  } else {
    p + theme(legend.position="none")
  }

}

p_k2 <- plot_fig3(2)
p_k4 <- plot_fig3(4)
p_k8 <- plot_fig3(8)
p_k16 <- plot_fig3(16)
p_k64 <- plot_fig3(64)
p_k64 <- plot_fig3(64, show_legend = T)

gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 5)
ggsave("plots/Fig3_k2.eps", p_k2, width = 6, height = 6)
ggsave("plots/Fig3_k4.eps", p_k4, width = 6, height = 6)
ggsave("plots/Fig3_k8.eps", p_k8, width = 6, height = 6)
ggsave("plots/Fig3_k16.eps", p_k16, width = 6, height = 6)
ggsave("plots/Fig3_k64.eps", p_k64, width = 6, height = 6)
ggsave("plots/Fig3_k64_legend.eps", p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

@@

df3_exp1b$p <- unlist(df3_exp1b$p) %>% round(3)
df4_exp2 <- df2_exp1b %>% group_by(type, restk) %>% do(ges=compute.des(.))
df4_exp2$ges <- unlist(df4_exp2$ges) %>% round(2)
df3_exp1b$ges <- df4_exp2$ges

df5_exp2 <- df2_exp1b %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
  group_by(type, restk) %>%
  summarize(acc_diff = accuracy[version == "fix distractors' k"] - accuracy[version == "fix target's k"])

@@

m <- matrix(df5_exp2$acc_diff, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1b$acc_diff <- as.vector(m)

@@

Test with baseline

```{r}
df_exp1b %>% group_by(type, restk,subject) %>% summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>% filter(accuracy <1) %>% do(t.test(.$accuracy, mu = .125) %>% broom::tidy()) %>% mutate(p.value = round(p.value, 3)) %>% knitr::kable()
```

@@

```{r load data - exp 2a}
load(here::here("..","data","exp2a","responses","responses_150410.RData"))
df_exp2a <- filter(df, block != 0) 
df_exp2a <- df_exp2a %>% mutate(restk = restk * 100, type = type * 100)
participants <- read.csv("../data/exp2/participants_171023.csv")
```

## Participant info
```{r exp3 participant info}
table(participants_exp3$gender)
c(mean(participants_exp3$age), sd(participants_exp3$age)) %>% round(2)
```

@@

```{r}
df_exp2a %>% group_by(restk) %>% summarize(accuracy_mean = mean(accuracy, na.rm = T) %>% round(2))
```

@@

```{r}
p1 <- df_exp2a %>%
  filter(restk == 2) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  geom_vline(xintercept = 2, linetype = 2) +
  scale_x_continuous("Target's speed (log scale)",breaks = c(0.5,1,2,3,4,6,8),labels = c("0.5","1","2","3","4","6","8"), trans = "log2") + 
  ggtitle("Slow-moving-distractors")
p2 <- df_exp2a %>%
  filter(restk == 4) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1)  + 
  ylab("Accuracy") + 
  ylim(0,1)+
  geom_vline(xintercept = 4, linetype = 2) +
  scale_x_continuous("Target's speed (log scale)",breaks = c(0.5,1,2,3,4,6,8),labels = c("0.5","1","2","3","4","6","8"), trans = "log2") + 
  ggtitle("Fast-moving-distractors")
gridExtra::grid.arrange(p1,p2, ncol = 2)

ggsave("plots/Figure4_slow.png", p1, width = 6, height = 6)
ggsave("plots/Figure4_fast.png", p2, width = 6, height = 6)
ggsave("plots/Figure4_slow.eps", p1, width = 6, height = 6)
ggsave("plots/Figure4_fast.eps", p2, width = 6, height = 6)
```

@@

```{r exp 3 - statistics}
df_exp2a %>% group_by(restk) %>% summarize(acc = mean(accuracy) * 100, sd = sd(accuracy) *100)
```

Difference between symmetrical cases
```{r}
df_sym <- df_exp2a %>% filter((restk == 2 & type == 4) |(restk == 4 & type == 2))
ez::ezANOVA(df_sym,
        dv=accuracy,
        wid = subject,
        within = restk)
ez::ezStats(df_sym,
        dv=accuracy,
        wid = subject,
        within = restk)

@@

Test with baseline

@@

```{r load data - exp 2b}
load("../data/exp2_fin/responses/responses_171023.RData")

df_exp2b <- filter(df, block != 0) 
df_exp2b <- df_exp2b %>% mutate(restk = restk * 100, type = type * 100)
rm(df)

participants_exp4 <- read.csv("../data/exp2_fin/participants_171023.csv")

df2_exp1bb <- rbind(df_exp2b, df_exp2b)
df2_exp1bb$version <- 2
df2_exp1bb$version[1:nrow(df_exp2b)] <- 1

# this is a little hack, just to make a correct ggplot with one line
tmp <- df_exp2b$restk
df2_exp1bb$restk[df2_exp1bb$version == 2] <- df_exp2b$type
df2_exp1bb$type[df2_exp1bb$version == 2] <- tmp

df2_exp1bb$version <- factor(df2_exp1bb$version, labels = c("fix distractors' speed", "fix target's speed"))
```

## Participant info
```{r exp4 - participants info}
table(participants_exp4$gender)
c(mean(participants_exp4$age), sd(participants_exp4$age)) %>% round(2)
```

@@

p_sp05 <- df2_exp1bb %>%
  filter(restk == .5) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = .5, linetype = 2) +
  ggtitle(expression("Fixed speed = 0.5"*degree*"/s"))

p_sp1 <- df2_exp1bb %>%
  filter(restk == 1) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 1, linetype = 2) +
  ggtitle(expression("Fixed speed = 1"*degree*"/s"))

p_sp2 <- df2_exp1bb %>%
  filter(restk == 2) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 2, linetype = 2) +
  ggtitle(expression("Fixed speed = 2"*degree*"/s"))

p_sp4 <- df2_exp1bb %>%
  filter(restk == 4) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 4, linetype = 2) +
  ggtitle(expression("Fixed speed = 4"*degree*"/s"))

p_sp8 <- df2_exp1bb %>%
  filter(restk == 8) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 8, linetype = 2) +
  ggtitle(expression("Fixed speed = 8"*degree*"/s"))

p_sp8_legend <- df2_exp1bb %>%
  filter(restk == 8) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 8, linetype = 2) +
  ggtitle(expression("Fixed speed = 8"*degree*"/s"))

gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 5)
ggsave("plots/Fig5_sp05.eps", p_sp05, width = 6, height = 6)
ggsave("plots/Fig5_sp1.eps", p_sp1, width = 6, height = 6)
ggsave("plots/Fig5_sp2.eps", p_sp2, width = 6, height = 6)
ggsave("plots/Fig5_sp4.eps", p_sp4, width = 6, height = 6)
ggsave("plots/Fig5_sp8.eps", p_sp8, width = 6, height = 6)
ggsave("plots/Fig5_sp8_legend.eps", p_sp8_legend, width = 6, height = 6)
# final plot was created in inkscape
```

@@

```{r compute the assymetry, warning=F}
df3_exp1bb <- df2_exp1bb %>% group_by(type, restk) %>% do(p=compute.p(.))

df3_exp1bb$p <- unlist(df3_exp1bb$p) %>% round(3)
df4_exp4 <- df2_exp1bb %>% group_by(type, restk) %>% do(ges=compute.des(.))
df4_exp4$ges <- unlist(df4_exp4$ges) %>% round(2)
df3_exp1bb$ges <- df4_exp4$ges

df5_exp4 <- df2_exp1bb %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
  group_by(type, restk) %>%
  summarize(acc_diff = accuracy[version == "fix distractors' speed"] - accuracy[version == "fix target's speed"])

m <- matrix(df3_exp1bb$ges, nrow = 5)
rownames(m) <- levels(df_exp2b$type)
colnames(m) <- levels(df_exp2b$type)
m[upper.tri(m,diag = T)] <- NA

df3_exp1bb$ges <- as.vector(m)

m <- matrix(df3_exp1bb$p, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1bb$p <- as.vector(m)

m <- matrix(df5_exp4$acc_diff, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1bb$acc_diff <- as.vector(m)

df3_exp1bb$target_lower_than_dist <- df3_exp1bb$acc_diff < 0
df3_exp1bb %>% filter(target_lower_than_dist)

df3_exp1bb %>% filter(p < 0.05)

differencies <- df3_exp1bb %>% filter(target_lower_than_dist)  %>% .$acc_diff *-1
differencies %>% range() %>% round(2)

>>>>

---
title: "manuscript - APP"
author: "Filip Dechterenko"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

@@

```{r load libraries, warning=F, message=F}

@@

data_pth <- here::here("..", "data")
plot_pth <- here::here("..", "plots")

if(!dir.exists(plot_pth)) {
  dir.create(plot_pth)
}
```

@@

```{r load data - exp 1a}
df_exp1a <- readRDS(file.path(data_pth,"exp1a","responses","responses_150330.rds")) %>% 
  filter(block != 0) %>% 
  filter(restk != "64") %>% # originally, we colledcted three levels of variaiblity, but the condition with kappa=64 showed similar results as kappa = 16
  as_data_frame() %>% 
  mutate(restk2 = recode(restk, `4` = "Brownian-like", `16` = "Ballistic-like"))

participants_exp1a <- read.csv(file.path(data_pth,"exp1a","participants_150526.csv"))

@@

```{r exp1 results accuracy}
df_exp1a %>% 
  group_by(restk) %>% 
  summarize(accuracy_mean = mean(accuracy, na.rm = T)) %>% 
  knitr::kable(digits = 2)

@@

```{r Figure 1}
traj_k64 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_64_rest4.csv")) %>% select(x = V1,y = V2) %>% as_data_frame()
p1 <- traj_k64 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15) +
  ggtitle("Ballistic-like")

traj_k4 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_4_rest4.csv")) %>% select(x = V3,y = V4) %>% as_data_frame()
p2 <- traj_k4 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15)+
  ggtitle("Brownian-like")
gridExtra::grid.arrange(p1,p2, ncol = 2)

ggsave(file.path(plot_pth, "Figure1_ballistic.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure1_brownian.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure1_ballistic.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure1_brownian.eps"), p2, width = 6, height = 6)
```

@@

@@

ggsave(file.path(plot_pth, "Figure2_brownian.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_ballistic.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_brownian.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_ballistic.eps"), p2, width = 6, height = 6)
```

```{r exp1a - fitting weibull}

@@

```{r exp 1a - overall differences, warning=F, message = F}
df_exp1a %>% 
  filter(restk2 == "Brownian-like") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

df_exp1a %>% 
  filter(restk2 == "Ballistic-like") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()
```

@@

```{r exp 1a - test vs baseline}
df_exp1a %>% 
  group_by(type, restk,subject) %>% 
  summarize(accuracy = mean(accuracy)) %>% 
  group_by(restk, type) %>% 
  filter(accuracy < 1) %>% 
  do(t.test(.$accuracy, mu = .125) %>% 
       broom::tidy()) %>% 
  mutate(p.value = round(p.value, 3)) %>% 
  knitr::kable()
```

## Difference between symmetrical cases
```{r exp1a - difference between symmetrical case, warning=F, message = F}
df_exp1a %>% 
  filter((restk == 4 & type == 16) |(restk == 16 & type == 4)) %>% 
  ez::ezANOVA(
        dv = accuracy,
        wid = subject,
        within = restk, 
        detailed = T) %>% 
  apa::anova_apa()

@@

```{r exp1b  - load data}
df_exp1b <- readRDS(file.path(data_pth,"exp1b","responses","responses_150622.rds")) %>% 
  filter(block != 0)

participants_exp1b <- read.csv(file.path(data_pth,"exp1b","participants_150526.csv"), fileEncoding = "UTF8")

@@

## Participant info
```{r}
table(participants_exp1b$gender)
c(mean(participants_exp1b$age), sd(participants_exp1b$age)) %>% round(2)
```

@@

```{r plots experiment 2}

p_k2 <- plot_fig3(2)
p_k4 <- plot_fig3(4)
p_k8 <- plot_fig3(8)
p_k16 <- plot_fig3(16)
p_k64 <- plot_fig3(64)
p_k64_legend <- plot_fig3(64, show_legend = T)

gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

@@

df3_exp1b$p <- unlist(df3_exp1b$p) %>% round(3)
df4_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(ges=compute.des(.))
df4_exp1b$ges <- unlist(df4_exp1b$ges) %>% round(2)
df3_exp1b$ges <- df4_exp1b$ges

df5_exp1b <- df2_exp1b %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
  group_by(type, restk) %>%
  summarize(acc_diff = accuracy[version == "fix distractors' k"] - accuracy[version == "fix target's k"])

@@

m <- matrix(df5_exp1b$acc_diff, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1b$acc_diff <- as.vector(m)

@@

## Test with baseline

```{r}
df_exp1b %>% 
  group_by(type, restk, subject) %>% 
  summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>%
  filter(accuracy < 1) %>% 
  do(t.test(.$accuracy, mu = .125) %>% 
       broom::tidy()) %>% 
  mutate(p.value = round(p.value, 3)) %>% 
  knitr::kable()
```

@@

```{r load data - exp 2a}
df_exp2a <- readRDS(file.path(data_pth,"exp2a","responses","responses_150410.rds")) %>% 
  filter(block != 0) %>% 
  mutate(restk = restk * 100, type = type * 100) %>% 
  mutate(restk2 = recode(restk, `2` = "Slow-moving-distractors", `4` = "Fast-moving-distractors"))

participants_exp2a <- read.csv(file.path(data_pth,"exp2a","participants_171023.csv"))
```

## Participant info

```{r exp2a - participant info}
table(participants_exp2a$gender)
c(mean(participants_exp2a$age), sd(participants_exp2a$age)) %>% round(2)
```

@@

```{r exp2a - results accuracy}
df_exp2a %>% 
  group_by(restk) %>% 
  summarize(accuracy_mean = mean(accuracy, na.rm = T)) %>% knitr::kable(digits = 2)
```

@@

```{r Figure 4}

p1 <- plot_fig4(2, ggtit = "Slow-moving-distractors")

p2 <- plot_fig4(4, ggtit = "Fast-moving-distractors")

ggsave(file.path(plot_pth, "Figure4_slow.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure4_fast.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure4_slow.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure4_fast.eps"), p2, width = 6, height = 6)
```

@@

```{r exp 2a - statistics}
df_exp2a %>% 
  group_by(restk) %>% 
  summarize(acc = mean(accuracy) * 100, sd = sd(accuracy) * 100) %>% 
  knitr::kable()
```

## Difference between symmetrical cases
```{r exp 2a - symmetrical case, warning=F, message=F}

df_exp2a %>% 
  filter((restk == 2 & type == 4) |(restk == 4 & type == 2)) %>% 
  ez::ezANOVA(
        dv = accuracy,
        wid = subject,
        within = restk, 
        detailed = T) %>% 
  apa::anova_apa()

df_exp2a %>% 
  filter((restk == 2 & type == 4) |(restk == 4 & type == 2)) %>%
  ez::ezStats(
        dv = accuracy,
        wid = subject,
        within = restk)

@@

## Test with baseline

@@

```{r exp 2b - load data}
df_exp2b <- readRDS(here::here("..", "data", "exp2b", "responses", "responses_171023.rds")) %>% 
 filter(block != 0)

df_exp2b <- df_exp2b %>% mutate(restk = restk * 100, type = type * 100)

participants_exp2b <- read.csv(here::here("..", "data", "exp2b", "participants_171023.csv"))

df2_exp2b <- rbind(df_exp2b, df_exp2b)
df2_exp2b$version <- 2
df2_exp2b$version[1:nrow(df_exp2b)] <- 1

# this is a little hack, just to make a correct ggplot with one line
tmp <- df_exp2b$restk
df2_exp2b$restk[df2_exp2b$version == 2] <- df_exp2b$type
df2_exp2b$type[df2_exp2b$version == 2] <- tmp

df2_exp2b$version <- factor(df2_exp2b$version, labels = c("fix distractors' speed", "fix target's speed"))
```

## Participant info
```{r exp2b - participants info}
table(participants_exp2b$gender)
c(mean(participants_exp2b$age), sd(participants_exp2b$age)) %>% round(2)
```

@@

p_sp05 <- plot_fig5(0.5)
p_sp1 <- plot_fig5(1)
p_sp2 <- plot_fig5(2)
p_sp4 <- plot_fig5(4)
p_sp8 <- plot_fig5(8)
p_sp8_legend <- plot_fig5(8, show_legend = T)

gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 3)
ggsave(file.path(plot_pth, "Fig5_sp05.eps"), p_sp05, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp1.eps"), p_sp1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp2.eps"), p_sp2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp4.eps"), p_sp4, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp8.eps"), p_sp8, width = 6, height = 6)
ggsave(file.path(plot_pth, "Fig5_sp8_legend.eps"), p_sp8_legend, width = 6, height = 6)
# final plot was created in inkscape
```

@@

```{r exp 2b - compute the assymetry, warning=F}
df3_exp2b <- df2_exp2b %>% group_by(type, restk) %>% do(p=compute.p(.))

df3_exp2b$p <- unlist(df3_exp2b$p) %>% round(3)
df4_exp2b <- df2_exp2b %>% group_by(type, restk) %>% do(ges=compute.des(.))
df4_exp2b$ges <- unlist(df4_exp2b$ges) %>% round(2)
df3_exp2b$ges <- df4_exp2b$ges

df5_exp2b <- df2_exp2b %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
  group_by(type, restk) %>%
  summarize(acc_diff = accuracy[version == "fix distractors' speed"] - accuracy[version == "fix target's speed"])

m <- matrix(df3_exp2b$ges, nrow = 5)
rownames(m) <- levels(df_exp2b$type)
colnames(m) <- levels(df_exp2b$type)
m[upper.tri(m,diag = T)] <- NA

df3_exp2b$ges <- as.vector(m)

m <- matrix(df3_exp2b$p, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp2b$p <- as.vector(m)

m <- matrix(df5_exp2b$acc_diff, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp2b$acc_diff <- as.vector(m)

df3_exp2b$target_lower_than_dist <- df3_exp2b$acc_diff < 0
df3_exp2b %>% filter(target_lower_than_dist) %>% knitr::kable()

df3_exp2b %>% filter(p < 0.05) %>% knitr::kable()

differencies <- df3_exp2b %>% filter(target_lower_than_dist)  %>% .$acc_diff *-1
differencies %>% range() %>% round(2)
